Reliable analytic approximation of pseudo-$\cl$ covariances

### 2019-05-18 draft/paper.tex
added all plots for sph case

In this sense, one can see in Fig.~\ref{fig:TTTT_EEEE_chi2} that, we fully
recover the $\chi^2$ distribution (defining $\chi^2 = \cl - \langle \cl
\rangle C^{-1} \cl - \langle \cl \rangle$) for the TTTT case; whereas for the
worst case (i.e. EEEE) we are able to recover its shape, although sifted
toward lower values. This might be consequence of the fact that the inverse of
the covariance matrix is biased. It is interesting to note that even
the approximation of the mixing matrix as that of the case with spin 0, gives
good results.

@@

@@

\begin{figure*} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_Efstathiou_TTTT_correlation_difference.png}~
  \includegraphics[width=\columnwidth]{./figures/run_sph_Efstathiou_EEEE_correlation_difference.png}
  \caption{Differences between the simulations and analytical approximation of
    the correlation matrices for the TTTT (left) and EEEE (right) cases.}
  \label{fig:TTTT_EEEE_chi2}
\end{figure*}

>>>>

In this sense, one can see in Fig.~\ref{fig:TTTT_EEEE_chi2} that, we fully
recover the $\chi^2$ distribution (defining $\chi^2 = \cl - \langle \cl
\rangle C^{-1} \cl - \langle \cl \rangle$) for the TTTT case; whereas for the
worst case (i.e. EEEE) we are able to recover its shape, although sifted
toward lower values. This might be consequence of the fact that the inverse of
the covariance matrix is biased. It is interesting to note that even
the approximation of the mixing matrix as that of the case with spin 0, gives
good results. The eigenvalues of the covariance matrix
(Fig.~\ref{fig:TTTT_EEEE_eigv}) are also recovered within the 1\%, for all
scales in the TTTT case, and for the smaller scales in the EEEE case. Finally,
the analytical approximations are shown to describe the scale coupling (see
Fig.~\ref{fig:TTTT_rows} that comes from the fact we are masking some regions
of the sky.

@@

\begin{figure*} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_ALL_TTTT_reldev_eigval.png}~
  \includegraphics[width=\columnwidth]{./figures/run_sph_ALL_EEEE_reldev_eigval.png}
  \caption{Comparison of the covariance matrix eigenvalues for the TTTT (left)
    and EEEE (right) cases.} 
  \label{fig:TTTT_EEEE_eigv}
\end{figure*}

\begin{figure} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_ALL_TTTT_rows_cov_matrix.png}~
  \caption{Mask induced scale correlations for the TTTT case.}
  \label{fig:TTTT_rows}
\end{figure}

@@

\begin{figure*} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_Efstathiou_TTTT_correlation_difference.png}~
  \includegraphics[width=\columnwidth]{./figures/run_sph_Efstathiou_EEEE_correlation_difference.png}
  \caption{Differences between the simulations and analytical approximation of
    the correlation matrices for the TTTT (left) and EEEE (right) cases.}
  \label{fig:TTTT_EEEE_corr}
\end{figure*}

These approximations do not work well for the B-modes, though. We can see in
Fig.~\ref{fig:BBBB} that we are not able to recover with accuracy the first
diagonal elements.

\begin{figure} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_ALL_BBBB_check_diagonal_terms_4.png}
  \caption{The analytical approximation are not able to reproduce accurately
    the terms involving the B-modes. Here we show the most extreme case, the
    corresponding to the BBBB modes.}
  \label{fig:BBBB}
\end{figure}
